### 2017-06-01 03-sequential-design.tex
Some text rephrasings

The MCMC-aMMSB algorithm that is the subject of this paper was initially
implemented in Python~\cite{LiAW15}, as is common
in the machine learning community.
We converted this implementation into an efficient sequential C++ application
to serve as a baseline for the parallel and distributed implementations.
We certainly do not consider this to be a contribution to the parallelization
of the algorithm, but for a fair analysis of the parallel implementations
a good baseline is necessary.

>>>>

The MCMC-aMMSB algorithm that is the subject of this paper was initially
implemented in Python~\cite{LiAW15}, as is common
in the machine learning community.
We converted this implementation into an efficient sequential C++ application
to serve as a baseline for the parallel and distributed implementations that
are the subject of the rest of this paper.
We certainly do not consider this sequential implementation to be a contribution to the parallelization
of the algorithm, but for a fair analysis of the parallel implementations
a good baseline is necessary.
